Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-10 article.tex
more explicit wording

Connectivity information between two neurons may be retrieved from successive
and slightly delayed burst events. At a local level, direct link
between two neurons will have shorter delay between fluorescence
peaks than undirected links. However, the fluorescence signal has a slow
decay compare to its rise. Therefore, we filter those unrelevant information
with a hard thresholding filter
\begin{align}
X^{\prime\prime\prime}_{t,i} &=
{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i
\label{eq:hard-treshold-filter}
\end{align}
where $f_3$ is a parameter of the hard-threshold filter and the $0.9$
exponent reduce the difference between peaks values.

>>>>

Connectivity information between two neurons may be retrieved from successive
and slightly delayed burst events. Direct links
between two neurons should have shorter delay between fluorescence
peaks than undirected links. However, the fluorescence signal has a slow
decay compare to its rise. Therefore, we filter those unrelevant information
with a hard thresholding filter
\begin{align}
X^{\prime\prime\prime}_{t,i} &=
{X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i
\label{eq:hard-treshold-filter}
\end{align}
where $f_3 \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
exponent reduce the difference between peaks values.
